Exploring Feature Engineering

### 2019-04-07 Scripts/evaluating_correlations.Rmd
editted results scripts

  if(cl=="GM12878"){
    countdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
                     resolution, 
                     "_count.rds",
                    sep="")
    percdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
                    resolution,
                    "_perc.rds",
                    sep="")
    distdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
                    resolution, 
                    "_dist.rds",
                    sep="")
  }else{
    countdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
                     resolution,
                     "_count.rds",
                    sep="")
    percdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
                    resolution,
                    "_perc.rds",
                    sep="")
    distdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
                    resolution,
                    "_dist.rds",
                    sep="")
    }

  countdata <- readRDS(countdir)
  percdata <- readRDS(percdir)
  distdata <- readRDS(distdir)

  #performing log2 transformation on distances
  distdata <- apply(distdata,2,function(x){log(x + 1, base=2)})

  if(cl=="K562"){
    countdata <- countdata[,-grep("Znf274", colnames(countdata))]
    percdata <- percdata[,-grep("Znf274", colnames(percdata))]
    distdata <- distdata[,-grep("Znf274", colnames(distdata))]
  }

  corrcount <- cor(countdata, method = "spearman")
  corrperc <- cor(percdata, method = "spearman")
  corrdist <- cor(distdata, method = "pearson")

  corrdata <- (corrcount + corrperc + corrdist)/3

@@

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/correlation_plots_unseparated/", 
                       cl, resolution,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  corrplot(corrdata,
         method="color",
         type="lower", 
         order="hclust", 
         tl.col="black", 
         #tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
  dev.off()

@@

#### Specific correlations

>>>>

  if(cl=="GM12878"){
    countdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
                     resolution, 
                     "_count.rds",
                    sep="")
    #percdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
    #                resolution,
    #                "_perc.rds",
    #                sep="")
    #distdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
    #                resolution, 
    #                "_dist.rds",
    #                sep="")
  }else{
    countdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
                     resolution,
                     "_count.rds",
                    sep="")
    #percdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
    #                resolution,
    #                "_perc.rds",
    #                sep="")
    #distdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
    #                resolution,
    #                "_dist.rds",
    #                sep="")
    }

  countdata <- readRDS(countdir)
  #percdata <- readRDS(percdir)
  #distdata <- readRDS(distdir)

  #performing log2 transformation on distances
  #distdata <- apply(distdata,2,function(x){log(x + 1, base=2)})

  if(cl=="K562"){
    countdata <- countdata[,-grep("Znf274", colnames(countdata))]
    #percdata <- percdata[,-grep("Znf274", colnames(percdata))]
    #distdata <- distdata[,-grep("Znf274", colnames(distdata))]
  }

  corrcount <- cor(countdata, method = "spearman")
  #corrperc <- cor(percdata, method = "spearman")
  #corrdist <- cor(distdata, method = "pearson")

  #corrdata <- (corrcount + corrperc + corrdist)/3
  corrdata <- corrcount

@@

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/correlation_plots_unseparated/", 
                       cl, resolution,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  corrplot(corrdata,
         method="color",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         #tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
  dev.off()

@@

#### Count overlap correlations
